Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-08-03 reports/manuscript.Rmd
Fix typo in abstract

abstract: |
  The influence of electronic screens on children and adolescents’ health and education is not well understood.
  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r targets::tar_read(manuscript_info)$effects_sum$sum_k` primary studies; `r targets::tar_read(manuscript_info)$effects_sum$sum_n` participants) on screen time and outcomes.
  `r targets::tar_read(manuscript_info)$effects_certain` effects from `r targets::tar_read(manuscript_info)$reviews_certain` meta-analyses met our criteria for statistical certainty.
  Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects `r targets::tar_read(manuscript_info)$abstract$range`.
  In education, results were mixed; for example, screen use was negatively associated with literacy `r targets::tar_read(manuscript_info)$abstract$lit_gen`, but this effect was positive when parents watched with their children `r targets::tar_read(manuscript_info)$abstract$coview`.
  In health, we found evidence for several small negative associations; for example, social media was associated with depression `r targets::tar_read(manuscript_info)$abstract$social_media`.
  Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in `r targets::tar_read(manuscript_info)$abstract$rob` included meta-analyses and high heterogeneity (`r manuscript_info$edu$n_i2`/`r manuscript_info$edu$n_certain` in education and `r manuscript_info$health$n_i2`/`r manuscript_info$health$n_certain` in health with $I^2 > 50\%$)
  We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.

>>>>

abstract: |
  The influence of electronic screens on children and adolescents’ health and education is not well understood.
  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r targets::tar_read(manuscript_info)$effects_sum$sum_k` primary studies; `r targets::tar_read(manuscript_info)$effects_sum$sum_n` participants) on screen time and outcomes.
  `r targets::tar_read(manuscript_info)$effects_certain` effects from `r targets::tar_read(manuscript_info)$reviews_certain` meta-analyses met our criteria for statistical certainty.
  Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects `r targets::tar_read(manuscript_info)$abstract$range`.
  In education, results were mixed; for example, screen use was negatively associated with literacy `r targets::tar_read(manuscript_info)$abstract$lit_gen`, but this effect was positive when parents watched with their children `r targets::tar_read(manuscript_info)$abstract$coview`.
  In health, we found evidence for several small negative associations; for example, social media was associated with depression `r targets::tar_read(manuscript_info)$abstract$social_media`.
  Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in `r targets::tar_read(manuscript_info)$abstract$rob` included meta-analyses and high heterogeneity (`r manuscript_info$edu$n_i2`/`r manuscript_info$edu$n_certain` in education and `r manuscript_info$health$n_i2`/`r manuscript_info$health$n_certain` in health with $I^2 > 50\%$).
  We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
